---
title: "Vignette for vedangpac"
author: "Vedang Vyas"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
---
output:
  md_document:
    variant: markdown_github
---

## vedangpac
This is a package created by me, Vedang Vyas, as a part of one of my assignments for STAT 545 at UBC. There are two functions in this package: **reordering()** and **factors_unordered()**. 

```{r}
library(devtools)
install_github("vedangvyas/vedangpac")
library(vedangpac)
```

### reorder()
**Purpose:** The purpose of this function is to take in a data frame and a factor, and reorder the data frame in a descending order with dependence on the factor.

**Example:**
```{r}
library(gapminder)
library(dplyr)
gtbl <- tbl_df(gapminder)
cont <- gtbl$continent
lifeexp <- gtbl$lifeExp
reordering(gtbl, cont)
reordering(gtbl, lifeexp)

```

### factors_unordered()
**Purpose:** The purpose of this function is to take in a vector and produce a factor where the levels are the vector entries but the factor produced has levels in the same order as they were in the vector. 

**Example:**
```{r}
fac <- c("A", "Hello", "Bob", "Apple")
factors_unordered(fac)
```


